Charged pion emission from neutron-rich heavy ion collisions for studies on the symmetry energy

### 2020-08-05 chapters_altFormat/ch_appendix.tex
added new format

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_NoEC_pimTotal}
         \caption{No efficiency correction.}
         \label{fig:pim_multCutVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_pimTotal}
         \caption{Efficiency corrected.}
         \label{fig:pim_multCutVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^-$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
\label{fig:pim_multCutVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_NoEC_pimTotal}
         \caption{Before efficiency correction.}
         \label{fig:pim_clustVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_pimTotal}
         \caption{After efficiency correction.}
         \label{fig:pim_clustVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^-$) when varying the number of cluster cut of the tracks.}
\label{fig:pim_clustVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_NoEC_pimTotal}
         \caption{No efficiency correction.}
         \label{fig:pim_cutVarPOCA_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_pimTotal}
         \caption{Efficiency corrected.}
         \label{fig:pim_cutVarPOCA_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^-$) when varying the dOCA cut.}
\label{fig:pim_cutVarPOCA}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_NoEC_pipTotal}
         \caption{No efficiency correction.}
         \label{fig:pip_multCutVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_pipTotal}
         \caption{Efficiency corrected.}
         \label{fig:pip_multCutVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
\label{fig:pip_multCutVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_NoEC_pipTotal}
         \caption{Before efficiency correction.}
         \label{fig:pip_clustVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_pipTotal}
         \caption{After efficiency correction.}
         \label{fig:pip_clustVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$) when varying the number of cluster cut of the tracks.}
\label{fig:pip_clustVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_NoEC_pipTotal}
         \caption{No efficiency correction.}
         \label{fig:pip_cutVarPOCA_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_pipTotal}
         \caption{Efficiency corrected.}
         \label{fig:pip_cutVarPOCA_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$) when varying the dOCA cut.}
\label{fig:pip_cutVarPOCA}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_NoEC_TotalRatio}
         \caption{No efficiency correction.}
         \label{fig:ratio_multCutVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{132Sn_Multiplicity_TotalRatio}
         \caption{Efficiency corrected.}
         \label{fig:ratio_multCutVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$)/Y($\pi^-$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
\label{fig:ratio_multCutVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_NoEC_TotalRatio}
         \caption{Before efficiency correction.}
         \label{fig:ratio_clustVar_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Clusters_TotalRatio}
         \caption{After efficiency correction.}
         \label{fig:ratio_clustVar_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$)/Y($\pi^-$) when varying the number of cluster cut of the tracks.}
\label{fig:ratio_clustVar}
\end{figure}

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_NoEC_TotalRatio}
         \caption{No efficiency correction.}
         \label{fig:ratio_cutVarPOCA_NoEC}
     \end{subfigure}
     \hfill
    \begin{subfigure}[b]{\textwidth}
         \centering
         \includegraphics[width=\textwidth]{POCA_TotalRatio}
         \caption{Efficiency corrected.}
         \label{fig:ratio_cutVarPOCA_EC}
     \end{subfigure}
     \hfill
\caption{Y($\pi^+$)/Y($\pi^-$) when varying the dOCA cut.}
\label{fig:ratio_cutVarPOCA}
\end{figure}

>>>>

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_NoEC_pimTotal} \label{fig:pim_multCutVar_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_pimTotal} \label{fig:pim_multCutVar_EC}}}%
	\caption{Y($\pi^-$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
	\label{fig:pim_multCutVar}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[Before efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_NoEC_pimTotal} \label{fig:pim_clustVar_NoEC}}}%
    \qquad
    \subfloat[After efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_pimTotal} \label{fig:pim_clustVar_EC}}}%
	\caption{Y($\pi^-$) when varying the number of cluster cut of the tracks.}
	\label{fig:pim_clustVar}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_NoEC_pimTotal} \label{fig:pim_cutVarPOCA_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_pimTotal} \label{fig:pim_cutVarPOCA_EC}}}%
	\caption{Y($\pi^-$) when varying the dOCA cut.}
	\label{fig:pim_cutVarPOCA}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_NoEC_pipTotal} \label{fig:pip_multCutVar_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_pipTotal} \label{fig:pip_multCutVar_EC}}}%
 	\caption{Y($\pi^+$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
	\label{fig:pip_multCutVar}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[Before efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_NoEC_pipTotal} \label{fig:pip_clustVar_NoEC}}}%
    \qquad
    \subfloat[After efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_pipTotal} \label{fig:pip_clustVar_EC}}}%
	\caption{Y($\pi^+$) when varying the number of cluster cut of the tracks.}
	\label{fig:pip_clustVar}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_NoEC_pipTotal} \label{fig:pip_cutVarPOCA_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_pipTotal} \label{fig:pip_cutVarPOCA_EC}}}%
	\caption{Y($\pi^+$) when varying the dOCA cut.}
	\label{fig:pip_cutVarPOCA}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_NoEC_TotalRatio} \label{fig:ratio_multCutVar_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{132Sn_Multiplicity_TotalRatio} \label{fig:ratio_multCutVar_EC}}}%
	\caption{Y($\pi^+$)/Y($\pi^-$) when varying the ${}^{132}$Sn charged particle multiplicity cut. }
	\label{fig:ratio_multCutVar}
\end{figure}

 \begin{figure}[!htb]%
    \centering
    \subfloat[Before efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_NoEC_TotalRatio} \label{fig:ratio_clustVar_NoEC}}}%
    \qquad
    \subfloat[After efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{Clusters_TotalRatio} \label{fig:ratio_clustVar_EC}}}%
	\caption{Y($\pi^+$)/Y($\pi^-$) when varying the number of cluster cut of the tracks.}
	\label{fig:ratio_clustVar}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[No efficiency correction.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_NoEC_TotalRatio} \label{fig:ratio_cutVarPOCA_NoEC}}}%
    \qquad
    \subfloat[Efficiency corrected.]{{\includegraphics[width=.46\textwidth,valign=c]{POCA_TotalRatio} \label{fig:ratio_cutVarPOCA_EC}}}%
	\caption{Y($\pi^+$)/Y($\pi^-$) when varying the dOCA cut.}
	\label{fig:ratio_cutVarPOCA}
\end{figure}
